\documentclass[11pt, oneside]{article} 
\usepackage{geometry}                		
\geometry{letterpaper}
\usepackage{graphicx}	
\usepackage{amssymb}

\title{Homework 3}
\author{Abhi Agarwal}
\date{}

\begin{document}
\maketitle

\section{Grammars}
\subsection{Question 1.1}
\par Explain why the following statement does not parse with a given grammar.
\par In the $matchedstmt$ part of the grammar - specifically in the $other$ there is nothing that follows it. In our statement we have a $if$ following the $other$, which is not permitted by the given grammar.
\par In more detail: $if$ $e$ $then$ would be parsed by the $matchedstmt$ part of grammar, and would follow another $matchedstmt$ - it would mean that if we have $other$ then it will stop. In the case of the test grammar it doesn't so it would not be able to be parsed, and therefore is incorrect.

\subsection{Question 1.2}
\par Show the grammar converted to right recursion?
\par \noindent The grammar being:
\par $lVal \rightarrow id \quad | \quad lVal \quad ( lVal ) \quad | \quad lVal \quad . \quad id$
\par \noindent Becomes:
\par $lVal \rightarrow id \quad lVal'$
\par $lVal' \rightarrow empty \quad | \quad (lVal) \quad lVal' \quad | \quad . \quad id \quad lVal'$

\subsection{Question 1.3}
\par Compute the FIRST and FOLLOW sets of this grammar.
\par \noindent FIRST:
\par It is simpler to start from letter then move towards trail for FIRST.
\par We will do this by: FIRST of trail is grade, FIRST of grade is letter, etc.
\par FIRST(letter) is the set of $\left\{ {A, B, C, F}\right\}$
\par FIRST(sign) is the set of $\left\{ {+, -, \epsilon}\right\}$
\par If the Production grade $ \rightarrow$  letter sign then add everything from FIRST(letter), but not from FIRST(sign) as we are looking for the FIRST. Therefore FIRST(grade) is the set of $\left\{ {A, B, C, F}\right\}$
\par The same applies for trail, and so the FIRST(trail) is the set of $\left\{ {A, B, C, F}\right\}$.
\par \noindent FOLLOW:
\par For FOLLOW we should move from the top down.
\par We put \$ in FOLLOW(trail) as it is the start symbol, and is not followed after anything. The set for FOLLOW(trail) is $\left\{ {\$}\right\}$
\par FOLLOW(grade) is $\left\{ {\$, \textrm{COMMA}}\right\}$
\par FOLLOW(sign) is $\left\{ {\$, \textrm{COMMA}}\right\}$
\par FOLLOW(letter) is $\left\{ {\$, -, +, \textrm{COMMA}}\right\}$ - no epsilon

\end{document}